Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-06-09 analysis/paper/paper.Rmd
added environmental data
added some codes for climate model

>>>>

## Paleo climate data
```{r}
library(ncdf4)
library(lattice)

# you'll need to get this file from
# https://figshare.com/articles/LateQuaternary_Environment_nc/12293345/3
# and move to our raw_data folder
file <- here::here("analysis/data/raw_data/LateQuaternary_Environment.nc")

env_nc      <- ncdf4::nc_open(file)
longitude   <- ncdf4::ncvar_get(env_nc, "longitude")
latitude    <- ncdf4::ncvar_get(env_nc, "latitude")
years       <- ncdf4::ncvar_get(env_nc, "time")
months      <- ncdf4::ncvar_get(env_nc, "month")
temperature <- ncdf4::ncvar_get(env_nc, "temperature")
biome       <- ncdf4::ncvar_get(env_nc, "biome")
ncdf4::nc_close(env_nc)

# this takes a few minutes
mean_annual_temperature <- apply(temperature, c(1, 2, 4), mean)

site_locations_tbl_temps <-
      korean_archaeological_site_locations %>% 
      dplyr::select(Site_name,
         lat_dd,
         long_dd) %>%
  rowwise()  %>%
  mutate(lonID = which.min(abs(longitude - long_dd)),
         latID = which.min(abs(latitude - lat_dd))) %>%
  mutate(mean_annual_temperature = list(tibble(year = years,
                                               mean_annual_temperature = mean_annual_temperature[lonID, latID, ]))) %>%
  unnest(mean_annual_temperature) %>%
  filter(between(year, -50000, -10000))
```
